Cell-type diversity and connectome of the ctenophore apical organ

### 2024-03-12 manuscript/Manuscript.qmd
Figure1

Figure1: (pic of a larva, boxed region of AO, schematic, catmaid pic with slice, dimensions, quadrants, regions)

@@

Figure2 - Balancer complex: balancer, lithocyte, groove 2 types, bridge - EM pics

@@

```{r, out.width = "100%", fig.cap="**Figure 1. Title fig 1** (A) legend (B) legend. " }
#| echo: false

>>>>

```{r, out.width = "100%", fig.cap="**Figure 1. Title fig 1** pic of a larva, boxed region of AO, schematic, catmaid pic with slice, dimensions, quadrants, regions, (A) legend (B) legend. " }
#| echo: false

@@

```{r, out.width = "100%", fig.cap="**Figure 2. Title fig 2** Balancer complex: balancer, lithocyte, groove 2 types, bridge - EM pics, (A) legend (B) legend. " }
#| echo: false

knitr::include_graphics("figures/Figure2.png")
```

@@
